% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Michael Zeng}{}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:michaelzeng7.at.icloud.com}{michaelzeng7\mbox{}@\mbox{}icloud.com}\sbull
(614) 800-7067\sbull
%\href{https://github.com/mzeng7}{github.com/mzeng7}\sbull
\href{https://www.linkedin.com/in/michael-z-78682812a/}{linkedin.com/in/michael-z-78682812a/}
\\
2732 Haste St\sbull
Apt 27\sbull
Berkeley, CA\sbull
United States

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Experience}

\headedsection
  {\href{https://www.friendlyrobots.co/}{Friendly Robots Company}}
  {\textsc{Berkeley, CA}} {%
  \headedsubsection
    {Software Engineering Intern}
    {June 2019 -- present}
    {\bodytext{Seed-stage startup headquartered in Berkeley, CA, whose mission is to develop autonomously driven robotic vacuum cleaners targeted at enterprises.
    \begin{itemize} 
		\item Implemented a path planning algorithm in Python designed to find the most optimal vacuuming path for a car-like robot given 2D map information generated from a laser (LiDAR) scanner.
		\item Integrated computer vision through a stereo camera in Robot Operating System (ROS) to allow the robot to detect and avoid obstacles while driving autonomously.
		\item Designed a basic website in HTML/Javascript allowing the user to teleoperate the robotic vacuum cleaner remotely through the Internet based on sensor and camera information.
	\end{itemize}
    }
    }
}

\spacedhrule{0.4em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{https://www.berkeley.edu/}{University of California, Berkeley}}
  {\textsc{Berkeley, CA}} {%
  \headedsubsection
    {B.A. \textnormal{(Computer Science)} \sbull GPA: \textnormal{3.775/4}}
    {Expected graduation: Spring 2021 \sbull August 2017 -- present}
    {\bodytext{\textbf{Major courses:}
    	\begin{itemize} 
		\item CS 61a: Structure and Interpretation of Computer Programs
		\item CS 61b: Data Structures
		\item CS 61c: Great Ideas in Computer Architecture (Machine Structures)
		\item CS 70: Discrete Mathematics and Probability Theory
	\end{itemize}	
	}}
}

\spacedhrule{0.4em}{-0.4em}

\roottitle{Projects}

\headedsection
  {CS 61b: Data Structures}
  {\headedsubsection
    {Languages: Java}
    {Fall 2018}
    {\bodytext{\begin{itemize}
    	\item \textbf{Galaxies:} Implemented a puzzle game 
	\item \textbf{Enigma:} Implemented an improved version of the Enigma machine, a German device used to encrypt messages during World War II.
	\item \textbf{Amazons:} Implemented a board game and an AI player, using a game tree to find the best moves.
	\item \textbf{Graphs:} Implemented a graphs utility package in Java, including a generalized graph traversal algorithm that can be extended to Depth-First Search, Breadth-First Search, Dijkstra's and A*.
	\end{itemize}}}
}

\headedsection
  {Prêt Allez}
  {\headedsubsection
    {Languages: JavaScript}
    {Summer 2018 -- present}
    {\bodytext{\begin{itemize}
	\item Implemented a web application which allows the user to construct a fencing referee's call based on the rules of right-of-way.
	\item In the future, users will be able to watch a fencing video, input what they would call if they were refereeing, and compare their input against what the referee in the video actually called.
	\end{itemize}}}
}

\spacedhrule{0.4em}{-0.4em}

\roottitle{Volunteer Work}

\headedsection
  {\href{https://fencing.berkeley.edu/}{Cal Fencing Club}}
  {\headedsubsection
    {Vice President}
    {August 2017 -- present}
    {\bodytext{\begin{itemize}
	\item As vice president, I assist the president in communicating information to the team, liaising with Cal Sports Clubs in organizing club events, and training to become president in 2020-21.
	\item The Cal Fencing Club manages a budget of more than \$20,000 per year.
	\item I am an officially rated foil referee for the United States Fencing Association.
	\end{itemize}}}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills and interests}

\inlineheadsection
  {Programming languages:}
  {Python 3, Java, JavaScript, C, RISC-V Assembly}
  
\inlineheadsection
  {Natural languages:}
  {English \emph{(native)}, German \emph{(intermediate)}, Mandarin Chinese \emph{(basic)}.}

\inlineheadsection
  {Interests:}
  {Fencing (attended nationals 4x), Wikipedia (administrator), Texas hold'em poker}


\end{document}

